### 2009-10-25 doc/manuals/user_interface/ui.tex
add note about previous incarnation of command names
First approach at updating and synchronizing the new CLI manual

%%%%---- Use EPS figures and graphics with LaTeX ----
%\usepackage{graphics}
%%%%---- USE PNG or JPG figures and graphicx with PDFLaTeX ----
\usepackage{graphicx}
\usepackage[linkbordercolor={0 0.8 0.8}]{hyperref}
\hypersetup{
  pdfauthor = {},
  pdftitle = {ARC Clients},
  pdfsubject = {User's manual},
  pdfkeywords = {Grid,KnowARC,ARC,client},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}

@@

   {\raggedleft NORDUGRID-MANUAL-?\par}

@@

The command line user interface of ARC consists of a set of commands
necessary for job submission and manipulation and data management. A
special utility also exists for test purposes.

@@

\section{Job submission and management} \label{sec:ui} 
\index{job management}
The following commands are used for job submission and management,
such as status check, results retrieval, cancellation, re-submission
and such. The jobs must be described using a job description language. ARC supports the languages JSDL, xRSL and JDL~\cite{xrsl}.

@@

\section{Test suite} \label{sec:testsuite}
%\input{arctest}

\section{Third-party commands} \label{sec:ui-other}
%\input{ui-other}

@@

\chapter{Configuration} \label{sec:client.conf} 
\section{ARC Client Configuration}
%\input{ui-conf}

>>>>

%%%%---- Use EPS figures and graphics with LaTeX ----
%\usepackage{graphics}
%%%%---- USE PNG or JPG figures and graphicx with PDFLaTeX ----
\usepackage{graphicx}
\usepackage[linkbordercolor={0 0.8 0.8}]{hyperref}
\hypersetup{
  pdfauthor = {ARC developers},
  pdftitle = {ARC Clients},
  pdfsubject = {User's manual},
  pdfkeywords = {Grid,KnowARC,ARC,NorduGrid,client},
  pdfcreator = {PDFLaTeX with hyperref package},
  pdfproducer = {PDFLaTeX}
}

@@

   {\raggedleft NORDUGRID-MANUAL-1\par}

@@

The command line user interface of ARC consists of a set of commands
necessary for job submission and manipulation and data management.
This manual replaces the older version of \texttt{NORDUGRID-MANUAL-1} and is
valid for ARC versions 0.9 and above. Command line tools semantics is the same
as in earlier versions of ARC, roughly following that of basic Linux commands
and most common batch system commands. One obvious difference is change of
the legacy prefix from ``ng'' to the more appropriate ``arc''. This is not only
a cosmetic change: \textbf{behaviour of the commands also have changed}, as did
their functionalities and options.
\begin{framed}
  Users are strongly discouraged from modifying their old scripts by
  simply replacing ``ng'' with ``arc'' -- results may be unpredictable.
\end{framed}

@@

\section{Job submission and management} \label{sec:ui} 
\index{job management}
The following commands are used for job submission and management,
such as status check, results retrieval, cancellation, re-submission
and such. The jobs must be described using a job description language. ARC
supports the following languages: JSDL~\cite{jsdl}, xRSL~\cite{xrsl} and
JDL~\cite{jdl}.

@@

%\section{Test suite} \label{sec:testsuite}
%\input{arctest}

%\section{Third-party commands} \label{sec:ui-other}
%\input{ui-other}

@@

\chapter{ARC Client Configuration} \label{sec:client.conf} 
\input{ui-conf}

### 2009-10-25 doc/tech_doc/xrsl/xrsl-urls.tex
First approach at updating and synchronizing the new CLI manual

\begin{tabular}{lp{10cm}}
   \verb#threads=<number># & specifies number of parallel
   streams to be used by GridFTP or HTTP(s,g); default value is 1,
   maximal value is 10\\
   \verb#cache=yes|no|renew|copy# & indicates whether the GM should
   cache the file; default for input files is \verb#yes#. \verb#renew#
   forces a download of the file, even if the cached copy is still valid.
   \verb#copy# forces the cached file to be copied (rather than linked) to
   the session dir, this is useful if for example the file is to be modified.\\
   \verb#readonly=yes|no# & for transfers to \verb#file://# destinations,
   specifies whether the file should be
   read-only (unmodifiable) or not; default is \verb#yes# \\
   \verb#secure=yes|no# & indicates whether the GridFTP data
   channel should be encrypted; default is \verb#no#\\
   \verb#blocksize=<number># & specifies size of
   chunks/blocks/buffers used in GridFTP or HTTP(s,g) transactions;
   default is protocol dependent\\ 
   \verb#checksum=cksum|md5|adler32# & specifies the algorithm for checksum to be
   computed (ev. provided to the indexing server). This is overridden
   by any metadata options specified (see below).\\ 
   \verb#exec=yes|no# & means the file should be treated as executable\\
   \verb#preserve=yes|no# & specify if file must be uploaded to this
   destination even if job processing failed (default is \verb#no#)\\
   \verb#guid=yes|no# & make software use GUIDs instead of LFNs while
   communicating to indexing services; meaningful for \verb#rls://#
   only\\
   \verb#overwrite=yes|no# & make software try to overwrite existing
   file(s), i.e. before writing to destination, tools will try to remove
   any information/content associated with specified URL\\
   \verb#protocol=gsi|gssapi# & to distinguish between two kinds of 
   \verb#httpg#. \verb#gssapi# stands for implemention using only GSSAPI 
   functions to wrap data and \verb#gsi# uses additional headers as 
   implmented in Globus IO\\
   \verb#spacetoken=<pattern># & specify the space token to be used for
   uploads to SRM storage elements supporting SRM version 2.2 or higher\\
   \verb#autodir=yes|no# & specify if before writing to specified location
   software should try to create all directories mentioned in specified
   URL. Currently this applies to FTP and GridFTP only. Default for those
   protocols is \verb#yes#\\
   \verb#tcpnodelay=yes|no# & controls the use of the TCP\_NODELAY
   socket option (which disables the Nagle algorithm). Applies to
   http(s) only. Default is \verb#no#\\ 
\end{tabular}

@@

$^1$This is a destination URL. The file will be copied to the GridFTP
server at se.domain.org with the path datapath/file25.dat and
registered in the RLS indexing service at grid.domain.org with the LFN
myfile02.dat.

$^2$This is a destination URL. The file will be copied to
srm.domain.org at the path griddir/file1 and registered to the LFC
service at lfc.domain.org with the LFN /user/file1. The given GUID
and checksum attributes will be registered.

$^3$This is a source URL. The file is registered in the LFC service at
lfc.domain.org with the given GUID and can be copied or queried by
this URL.

>>>>

\begin{longtable}{lp{10cm}}
   \verb#threads=<number># & specifies number of parallel
   streams to be used by GridFTP or HTTP(s,g); default value is 1,
   maximal value is 10\\
   \verb#cache=yes|no|renew|copy# & indicates whether the GM should
   cache the file; default for input files is \verb#yes#. \verb#renew#
   forces a download of the file, even if the cached copy is still valid.
   \verb#copy# forces the cached file to be copied (rather than linked) to
   the session dir, this is useful if for example the file is to be modified.\\
   \verb#readonly=yes|no# & for transfers to \verb#file://# destinations,
   specifies whether the file should be
   read-only (unmodifiable) or not; default is \verb#yes# \\
   \verb#secure=yes|no# & indicates whether the GridFTP data
   channel should be encrypted; default is \verb#no#\\
   \verb#blocksize=<number># & specifies size of
   chunks/blocks/buffers used in GridFTP or HTTP(s,g) transactions;
   default is protocol dependent\\
   \verb#checksum=cksum|md5|adler32|no# & specifies the algorithm for checksum to be
   computed (for transfer verification or provided to the indexing server). This is overridden
   by any metadata options specified (see below). If this option is
   not provided, the default for the protocol is used. \verb#checksum=no#
   disables checksum calculation.\\
   \verb#exec=yes|no# & means the file should be treated as executable\\
   \verb#preserve=yes|no# & specify if file must be uploaded to this
   destination even if job processing failed (default is \verb#no#)\\
   \verb#guid=yes|no# & make software use GUIDs instead of LFNs while
   communicating to indexing services; meaningful for \verb#rls://#
   only\\
   \verb#overwrite=yes|no# & make software try to overwrite existing
   file(s), i.e. before writing to destination, tools will try to remove
   any information/content associated with specified URL\\
   \verb#protocol=gsi|gssapi# & to distinguish between two kinds of 
   \verb#httpg#. \verb#gssapi# stands for implemention using only GSSAPI 
   functions to wrap data and \verb#gsi# uses additional headers as 
   implmented in Globus IO\\
   \verb#spacetoken=<pattern># & specify the space token to be used for
   uploads to SRM storage elements supporting SRM version 2.2 or higher\\
   \verb#autodir=yes|no# & specify if before writing to specified location
   software should try to create all directories mentioned in specified
   URL. Currently this applies to FTP and GridFTP only. Default for those
   protocols is \verb#yes#\\
   \verb#tcpnodelay=yes|no# & controls the use of the TCP\_NODELAY
   socket option (which disables the Nagle algorithm). Applies to
   http(s) only. Default is \verb#no#\\ 
\end{longtable}

@@

$^1$This is a destination URL. The file will be copied to the GridFTP
server at \texttt{se.domain.org} with the path \texttt{datapath/file25.dat} and
registered in the RLS indexing service at \texttt{grid.domain.org} with the LFN
\texttt{myfile02.dat}.

$^2$This is a destination URL. The file will be copied to
\texttt{srm.domain.org} at the path \texttt{griddir/file1} and registered to the LFC
service at \texttt{lfc.domain.org} with the LFN \texttt{/user/file1}. The given GUID
and checksum attributes will be registered.

$^3$This is a source URL. The file is registered in the LFC service at
\texttt{lfc.domain.org} with the given GUID and can be copied or queried by
this URL.
